rbcL community comparison

### 2019-11-05 code/rbcl_community_compare.Rmd
minor changes, re-made diversity plots as 2 panel

```{r, echo=F}
faith_elev_plot <- ggplot(faiths, aes(y=PD, x=elev_m))+
  geom_point() +
  geom_smooth(method = "lm")+
  geom_text_repel(aes(label=alias))+
  labs(title="Phylogenetic diversity of snow algae rbcL vs elevation",y="Faith's phylogenetic diversity (PD)",x="Elevation (m)")
faith_elev_plot
```

@@

# plot diversity of samples
ggplot(otu_diversity, aes(x=elev_m, y=shannon))+
  geom_point() +
  geom_text_repel(aes(label=alias)) +
  geom_smooth(method = "lm")
```

@@

```{r output, include=F}
ggsave(filename = here("manuscript/figs/3_community/combined_fig_3.png"), plot=combined_fig_3, height=10, width=7)
ggsave(filename = here("manuscript/figs/supplementary/diversity.png"), plot = faith_date_plot, height = 5, width = 7)
```

>>>>

```{r, echo=F}
faith_elev_plot <- ggplot(faiths, aes(y=PD, x=elev_m))+
  geom_point() +
  geom_smooth(method = "lm")+
  geom_text_repel(aes(label=alias))+
  labs(y="Faith's phylogenetic diversity (PD)",x="Elevation (m)", tag="B")
faith_elev_plot
```

@@

# plot diversity of samples
shannon <- ggplot(otu_diversity, aes(x=elev_m, y=shannon))+
  geom_point() +
  geom_text_repel(aes(label=alias)) +
  geom_smooth(method = "lm")+
  labs(y="Shannon diversity", tag="A")+
  theme(axis.title.x = element_blank())
shannon
```

```{r diversity_plots, include=F}
diversity_plots <- gridExtra::grid.arrange(shannon, faith_elev_plot, nrow=2)

@@

```{r output, include=F}
ggsave(filename = here("manuscript/figs/3_community/combined_fig_3.png"), plot=combined_fig_3, height=10, width=7)
ggsave(filename = here("manuscript/figs/diversity.png"), plot = diversity_plots, height = 10, width = 7)
```
